### 2017-06-05 manuscript/usses_water_ms.Rmd
more results and writing

\begin{align}
\mu_{i(j(k))} &= \beta_{0,j(k)} + \beta_{1,j(k)}x_i, \\
y_{i(j(k))} &\sim \mathcal{N} \left(\mu_{i(j(k))}, \sigma^2_{k} \right),
\end{align}

@@

The intercept and slope terms are modeled hierarchichally to account for the non-independence of observations across years within plots and to allow us to test the hypothesis that our treatments alter the ANPP-precipitation relationship.
As noted above, plot-level coefficients are drawn from treatment-level coeffecients, which are drawn from overall coefficients.
We also include a covariance structure among the intercept and slope at each level.
Formally, our hierarhical structure is as follows.
Note that we drop the intercept (0) and slope (1) subscripts and instead refer to a vector of coefficients, $\boldsymbol{\beta}$.

@@

\begin{align}
\boldsymbol{\beta}_{j(k)} &\sim \mathcal{N} \left( \boldsymbol{\beta}_k, \Sigma(k) \right), \\
\boldsymbol{\beta}_{k} &\sim \mathcal{N} \left( \boldsymbol{\beta}, \Sigma  \right), \\
\boldsymbol{\beta} &\sim \mathcal{N} \left( 0, 1 \right).
\end{align}

@@

All R code and data necessary to reproduce our analysis has been archived on Figshare (\emph{link here after acceptance}) and released on GitHub (https://github.com/atredennick/usses_water/releases/v0.1).
We also include annotated Stan code in our model description in Appendix 1.

Results
-------
Three of our five treatment years fell in years of below average rainfall (Fig. 1A).
Thus, those three years represent a lower magnitude of absolute change in precipitation experienced by the treatments.
Averaged across treatments, ANPP varied from a minimum of xxx g m$^{-2}$ in 2014 to a maximum of xxx g m$^{-2}$ in 2016 (Fig. 1B).
ANPP was slightly higher in irrigation plots and slightly lower in drought plots (Fig. 1B), corresponding to estimated soil volumetric water content (VWC) differences among treatments (Fig. 1C).
Such differences in soil VWC indicate our treatment infrastructure was successful.

Growing season precipitation had a positive effect on ANPP (mean of $\beta_{1}$ = 0.67; 80\% BCI = 0.24, 1.10; 95\% BCI = -0.11, 1.34).
Average ANPP was similar among treatments (similar intercepts, Fig. 2A), as was the effect of precipitation (similar slopes, Fig. 2B).
In an average precipitation year (i.e., $x$ = 0 in Eq. 1), the probability that ANPP in a drought plot is less than ANPP in a control plot was 0.58, and the probability that ANPP in an irrigation plot is higher than in a control plot was 0.57.
In other words, the posterior values of $\beta_0(\text{control}) - \beta_0(\text{drought})$ and $\beta_0(\text{control}) - \beta_0(\text{drought})$ broadly overlapped zero.
There was also no evidence that the treatment effects became more important over time because differences between average treatment and control plots were centered on zero regardless of year of the experiment (Fig. 3).

@@

Discussion
----------

@@

Tables
------

@@

>>>>

\begin{align}
\mu_{i(j(k))} &= \beta_{0,j(k)} + \beta_{1,j(k)}x_i, \\
y_{i(j(k))} &\sim \text{Normal} \left(\mu_{i(j(k))}, \sigma^2_{k} \right),
\end{align}

@@

The intercept and slope terms are modeled hierarchichally to account for the non-independence of observations across years within plots and to allow us to test the hypothesis that our treatments alter the ANPP-precipitation relationship.
As noted above, plot-level coefficients are drawn from treatment-level coeffecients, which are drawn from overall coefficients.
We also include a covariance structure among the intercept and slope at each level.
Formally, our hierarhical structure is as follows, where we drop the intercept (0) and slope (1) subscripts and instead refer to a vector of coefficients, $\boldsymbol{\beta}$:

@@

\begin{align}
\boldsymbol{\beta}_{j(k)} &\sim \text{MVN} \left( \boldsymbol{\beta}_k, \Sigma(k) \right), \\
\boldsymbol{\beta}_{k} &\sim \text{MVN} \left( \boldsymbol{\beta}, \Sigma  \right), \\
\boldsymbol{\beta} &\sim \text{Normal} \left( 0, 1 \right),
\end{align}

\noindent{} where $\boldsymbol{\beta}_{j(k)}$ is the vector of regression coefficients (intercept and slope) for plot *j* associated with treatment *k*, $\boldsymbol{\beta}_{k}$ is the vector of coefficients for each treatment, and $\boldsymbol{\beta}$ is the vector of overall coefficients.
The plot- and treatment-level coefficients are drawn from multivariate normal distributions with covariance matrix $\Sigma$.
For the plot-level coefficients, each treatment has its own variance-covariance matrix (i.e., $\Sigma(k)$).
The overall coefficients are drawn from a normal prior with mean 0 and standard deviation 1.
A full description of model is in Appendix 2.

@@

All R code and data necessary to reproduce our analysis has been archived on Figshare (\emph{link here after acceptance}) and released on GitHub (https://github.com/atredennick/usses_water/releases/v0.1).
We also include annotated Stan code in our model description in Appendix 2.

Results
-------
Three of our five treatment years fell in years of below average rainfall (Fig. 1A).
Thus, those three years represent a lower magnitude of absolute change in precipitation experienced by the treatments.
Averaged across treatments, ANPP varied from a minimum of 74.5 g m$^{-2}$ in 2014 to a maximum of 237.1 g m$^{-2}$ in 2016 (Fig. 1C).
ANPP was slightly higher in irrigation plots and slightly lower in drought plots (Fig. 1C), corresponding to estimated soil volumetric water content (VWC) differences among treatments (Fig. 1B).
Such differences in soil VWC indicate our treatment infrastructure was successful.

Growing season precipitation had a positive effect on ANPP (mean of $\beta_{1}$ = 0.67; 80\% BCI = 0.24, 1.10; 95\% BCI = -0.11, 1.34) (Fig. 1D).
Average ANPP was similar among treatments (similar intercepts, Fig. 2A), as was the effect of precipitation (similar slopes, Fig. 2B).
In an average precipitation year (i.e., $x$ = 0 in Eq. 1), the probability that ANPP in a drought plot is less than ANPP in a control plot was 0.58, and the probability that ANPP in an irrigation plot is higher than in a control plot was 0.57.
In other words, the posterior distributions of $\beta_0(\text{control}) - \beta_0(\text{drought})$ and $\beta_0(\text{control}) - \beta_0(\text{drought})$ broadly overlapped zero.
There was also no evidence that the treatment effects became more important over time because differences between average treatment and control plots were centered on zero regardless of year of the experiment (Fig. 3).

@@

Discussion
----------
We manipulated growing season precipitation for five years in a sagebrush steppe to reach the extremes of the historical distribution of precipitation (Fig. 1A).
In so doing, we aimed to understand how this ecosystem might respond to periods of relatively novel precipitation regimes.
Our results suggest that ecosystem functioning, as measured by annual net primary productivity, and community composition are not sensitive to the precipitation manipulations we imposed.

@@

<!---
Tables
------

@@

--->
